---
title: "Assignment 2"
author: "Rachel Stagner"
date: today
date-format: medium
format: html
---

## Task 1

**To complete this task, first I loaded the tidyverse library.**

```{r}
#| message: false
library(tidyverse) #load tidyverse library
```

**Then, I used the readr package to load the college.data.csv file into an object called college_data.** 

```{r}
college_data <- read_csv("./data/collegedata.csv") #load collegedata.csv
```

## Task 2

**Even though the read_csv command gives you a message with the number of rows and columns, you can also use the dplyr command "glimpse" to see these details:**

```{r}
glimpse(college_data) #view the rows and column information for the dataframe
```

**Using either method, we find out that there are 7175 rows and 12 columms in this dataframe.**

## Task 3 

**To create a new dataframe with only certain columns, we can use the dplyr command "select" to choose the requested columns: INSTNM, SAT_AVG, and ADM_RATE.**

```{r}
#create a new dataframe that has the requested columns
admission_rates <- college_data |> select(INSTNM, SAT_AVG, ADM_RATE)
```

**I like to confirm that everything worked as I wanted by running the head or glimpse command to verify.**

```{r}
#confirming the new dataframe:
glimpse(admission_rates)
```

