---
title: "Assignment 2"
author: "Rachel Stagner"
date: today
date-format: medium
format: html
---

## Task 1

**To complete this task, first I loaded the tidyverse library.**

```{r}
#| message: false
library(tidyverse) #load tidyverse library
```

**Then, I used the readr package to load the college.data.csv file into an object called college_data with the `read_csv()` command** 

```{r}
college_data <- read_csv("./data/collegedata.csv") #load collegedata.csv
```

## Task 2

**Even though the `read_csv()` command gives you a message with the number of rows and columns, you can also use the dplyr command `glimpse()` to see these details:**

```{r}
glimpse(college_data) #view the rows and column information for the dataframe
```

**Using either method, we find out that there are 7175 rows and 12 columms in this dataframe.**

## Task 3 

**To create a new dataframe with only certain columns, we can use the dplyr command `select()` to choose the requested columns: INSTNM, SAT_AVG, and ADM_RATE.**

```{r}
#create a new dataframe that has the requested columns
admission_rates <- college_data |> select(INSTNM, SAT_AVG, ADM_RATE)
```

**I like to confirm that everything worked as I wanted by running the `head()` or `glimpse()` command to verify.**

```{r}
#confirming the new dataframe:
glimpse(admission_rates)
```

## Task 4

**First, I created a new dataframe with the NA rows removed, using the `drop_na()` command from the tidyr package, and `glimpse()` to confirm my changes.**

```{r}
cleaned_data <- admission_rates |> drop_na() #drop rows with NA values
glimpse(cleaned_data) #confirm dropped values
```

**Then, I used `ggplot()` from the ggplot2 library to create a scatter plot of Average SAT scores versus Admission Rates. I styled it a bit with blue points and the black and white theme, and added axes labels and a title and subtitle.**

**Interestingly, it took me a minute to figure out what this data was telling me, but when I thought about it, it makes sense.  The higher the school's average SAT score, the lower their admission rate due to their high selectivity.**
```{r}
#create a new plot of SAT scores versus admission rate
  ggplot(cleaned_data, aes(x = SAT_AVG, y = ADM_RATE)) + #create the plot
  geom_point(color="blue") +
  labs(x = "Average SAT Score", #apply labels
       y = "Admission Rate", 
       title = "Average SAT Scores versus Admission Rates",
       subtitle = "Each point is an individual college or university") +
  theme_bw() #apply theme
```

