---
title: "Tidyverse Solution"
author: "Rachel Stagner"
date: today
format: 
  html:
    embed-resources: True
editor: visual
---

```{r}
#| message: false
#| warning: false
if(!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, gapminder, broom)
```


## Problem 1

We were asked to create a dataframe, `df`, using the following code:

```{r}
tribble( ~x,    ~y,    ~w,    ~z,
              210,   300,   220,   180,
              102,   100,   119,   187,
              176,   175,   188,   173,
              87,    95,   91,     94,
              202,   210,  234,    218,
              110,   122,  131,    128,
) -> dt
```

### 1a.  

Use the `map()` function from the `purr` package in tidyverse to find the mean of each column of the dataframe `dt`.

```{r}
dt_mean <- map(dt, mean) #uses the 'map' function to find the mean 
dt_mean #prints the mean
```

### 1b.

Use the `map()` function to find the standard deviation of each column in the dataframe `dt`.

```{r}
dt_sd <- map (dt, sd) #uses 'map' to find the sd of each column
dt_sd #print the result
```

### 1c.

Use the `map_df()` function to calculate the square root for each value in the dataframe `dt`. This function returns the results in another dataframe. 

```{r}
dt_sqrt <- map_df(dt, sqrt) #find the square root of each value
dt_sqrt #print the resulting df
```

### 1d.

Use the `summary()` function to find the min, max, mean, median, 1st and 3rd quartile of the columns of the dataframe.  This is a base R function.  

```{r}
summary(dt) #use the summary function in base r to calculate summary stats for dt

```

The `echo: false` option disables the printing of code (only output is displayed).
